\sysfull

### 2017-08-11 paper/coalescing.tex

\noindent\textbf{Task Coalescing Implementation:} Figure~\ref{fig:coalescing_example} illustrates how \sys coalesces tasks. Figure~\ref{fig:coalescing_example_states} (left) shows a sequence of three tasks executing in \sys with no coalescing, incurring the cost of commit at each task transition. The same figure shows the same sequence of tasks executing as coalesced groups of three tasks $C=2$ (center) and $C=3$ (right). Figure~\ref{fig:coalescing_example_flowchart} shows how \sys adapts the value of $C$ based on $S$. \sys executes eight tasks in the first operating period, assigning the half of previous $C=8/2$. \sys completes only two of the four coalesced tasks in the next operating period and then power fails. \sys sets $C=(6+8+2)/2$ in the next operating period, coalescing pairs of tasks and successfully committing two pairs before power fails. Execution resumes at the start of the third pair of tasks with a coalescing factor of two. If a larger number of tasks successfully complete in the next operating period, i.e., $S$ is larger, $C$ correspondingly increases, allowing more aggressive coalescing.\todo{Rewrite this paragraph to reflect what is in the figure}{Przemek}

>>>>

\noindent\textbf{Task Coalescing Implementation:} Figure~\ref{fig:coalescing_example} illustrates how \sys coalesces tasks. Figure~\ref{fig:coalescing_example_states} (left) shows a sequence of three tasks executing in \sys with no coalescing, incurring the cost of commit at each task transition. The same figure shows the same sequence of tasks executing as coalesced groups of three tasks $C=2$ (center) and $C=3$ (right). Figure~\ref{fig:coalescing_example_flowchart} shows how \sys adapts the value of $C$ based on $S$. \sys executes tasks in the first operating period, assigning the \emph{half of sum of all previous $S$ periods} (in the example case: $C=8/2$). \sys completes then coalesced tasks successfully (four tasks were executed) and in the next operating period, i.e. $C=(8+4)/2$. In the third task execution, power fails after the second task. Then \sys re-executes coalesced task since the previous failure and sets $C=(6+8+2)/2$ in the next operating period. If a larger number of tasks successfully complete in the next operating period, i.e., $S$ is larger, $C$ correspondingly increases, allowing more aggressive coalescing.
